Estimating Uncertainty for Tipping Points with Deep Learning

### 2022-05-12 manuscript/manuscript.Rmd
bullet pts for discussion

reflects a fundamental challenge of ecological forecasting.

>>>>

- overall forecasting bifurcations is difficult, even in the idealized case of ample measurement data and knowing the structural model exactly.

- ML techniques are mostly bracketed by ARIMA and MCMC as expected (better than arima, worse than estimates using true model), though details vary (can do better than MCMC etc).

- MCMC is most relevant to the saddle-node, which is an especially hard problem for the model-free methods.  block rnn does surprisingly well here all things considered.

- the stochastic context is in some sense the easiest for  ML/statistical methods, as it is the only case where training data includes the phenomenon of the transition.

- MCMC does not always out-perform ML techniques, particularly in CRPS terms. Log likelihood-based skill score

- Forecast skill assessment can be challenging. it is essential to pay attention to skill over time. Forecast error is not a smooth function of horizon, nor is it always increasing with longer horizons.

- Examining means and summary statistics of variation (confidence intervals) can be limiting too, obscuring aspects such as bimodally distributed scores.
